Review Manuscript

### 2019-04-04 review_article.Rmd
additional author notes included in paper

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!--
Author notes:
6000 words maximum.
focused  application  of  literature  to address  a  relevant  clinical  issue:
Mapping cancer outcomes
Cartogram applications should point to examples of cancer outcomes, with the main cartogram section discussing sources considered in grey literature review. Examples of political areas may be considered if cancer data is aggregated at these levels.

Future steps should consider applications not currently utilised for cancer outcome displays, where their use may improve decision making
-->

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!--
Author notes:
6000 words maximum.
focused  application  of  literature  to address  a  relevant  clinical  issue:
Mapping cancer outcomes
All cartogram applications should point to examples of cancer outcomes, with the main cartogram section discussing sources considered in grey literature review

Future steps should consider applications not utilised for cancer outcome displays, where their use may improve decision making
-->
